---
title       : Estimate Miles per US gallon
subtitle    : Presenting a shiny application
author      : sdd1012
job         : Specializing in Data Science
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Objective 

1.      Create an interactive shiny application that predicts MPG

2.      Prepare a prediction model

3.      Publish the shinyapps website


--- .class #id bg:white

## Approach 

*  The prediction model uses R dataset **mtcars**

```{r, echo=FALSE, results='hide'}
library(ggplot2)
data(mtcars)
mtcars$am<- factor(mtcars$am)
mtcars$cyl<- factor(mtcars$cyl)
mtcars$wt<- mtcars$wt*1000
```

*  Linear regression is used as method
$Y = a_0 + a_1*X_1 + a_2*X_2 + ...+ a_n*X_n$

*  The features "weight", "cylinder type", "gross horsepower", "transmission type" are chosen for exploration

*  The sum of Squared Error(SSE) is used
SSE = $\sum(Y_f-Y_a)^2$ where $Y_f$ is fitted and $Y_a$ is actual

--- .class #id bg:white

## Some exploratory results 

```{r, echo=FALSE, fig.height=3, fig.width=7, results='asis'}
qplot(wt,mpg,data=mtcars, geom=c("point","smooth"), method="lm")

```

*       SSEs for linear models

```{r, echo=FALSE, results='asis'}
fitWt<- lm(mpg~wt,data=mtcars)
fitWtHp<- lm(mpg~wt+hp, data=mtcars)
fitWtAm<- lm(mpg~wt+am, data=mtcars)
fitWtHpCyl<- lm(mpg~wt+hp+cyl, data=mtcars)
sprintf("formula = mpg ~ wt: %.2f", round(sum(resid(fitWt)^2),2))
```

```{r, echo=FALSE, results='asis'}
sprintf("formula = mpg ~ wt+hp: %.2f", round(sum(resid(fitWtHp)^2),2))
```

```{r, echo=FALSE, results='asis'}
sprintf("formula = mpg ~ wt+am: %.2f", sum(resid(fitWtAm)^2))
```


```{r, echo=FALSE, results='asis'}
sprintf("formula = mpg ~ wt+hp+cyl: %.2f", sum(resid(fitWtHpCyl)^2))
```

--- .class #id bg:white

## The shiny app and the Code

*       The link of the shiny app is

[http://sdd1112.shinyapps.io/shiny](http://sdd1112.shinyapps.io/shiny) 


*       The github link for the code is

[https://github.com/sdd1012/shiny](https://github.com/sdd1012/shiny) 

